---
title: "Demographics and cognitive tests"
author: "Bindoff, A."
date: "17/06/2020"
output: 
  html_document:
    code_folding: 'hide'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r}
library(ggplot2)
library(dplyr)
library(table1)


d0 <- readRDS('baseline_20200617.rds')
long0 <- readRDS('thbp_7yr_long_20200617.rds')

```

## Demographics {.tabset}

### Baseline

Exclusions:  participants who nominated membership in intervention group who did not complete two or more university units (25% FTE), participants in control group who completed any university study after the study began, and any participants who were higher degree by research candidates (indicating recent university study).  


```{r}
table1(~age_1 + age_group + gender + all_courses_post2010_cp + wtar_fsiq + mhq_edschool + pcr | group,
       d0,
       render.continuous = c(.= "Mean (SD)", .= "Median [Q1, Q3]"),
       overall = FALSE)
```

### At each assessment  

```{r}


table1(~age_1 + age_group + gender + group + pcr | title*phase_f,
       group_by(long0, phase_f) %>% filter(!duplicated(idcode)),
       overall = FALSE,
       render.continuous = c(.= "Mean (SD)"))
```


```{r}
att_t6 <- round(1-(1+(308-485)/485)^(1/5),3)*100
att_t8 <- round(1-(1+(149-485)/485)^(1/7),3)*100

```

Annualised attrition up to assessment at year 5 was `r att_t6`% *p.a.*, and counting incomplete assessments at year 7, `r att_t8`% *p.a.*.  


## Cognitive tests

```{r}

test_names <- c(
  `ravlt_t15_tot_z` = "RAVLT tot",
  `ravlt_arcl_raw_z` = "RAVLT rcl",
  `rcft_rcl_raw_z` = "RCFT",
  `lmi_unit_tot_z` = "LMi",
  `lmii_unit_tot_z` = "LMii",
  `reversed_log_pal_te6_score_z` = "PAL te6",
  `cowat_tot_z` = "COWAT",
  `wais_ds_raw_z` = "WAIS ds",
  `reversed_log_tmt_b_time_z` = "TMT-B",
  `pal_ftm_score_z` = "PAL ftm",
  `ssp_len_z` = "SSP length",
  `ssp_te_z` = "SSP tot errors",
  `reversed_log_swm_be_z` = "SWM be",
  `reversed_log_stroop_c_time_z` = "STROOP C time",
  `rvp_a_z` = "RVP-A",
  `reversed_log_bnt_raw_z` = "BNT",
  `wais_com_raw_z` = "WAIS comp",
  `wais_lns_raw_z` = "WAIS lns",
  `reversed_log_wais_voc_raw_z` = "WAIS voc",
  `-1.1` = "55 years of age",
  `0.3` = "65 years of age",
  `1.7` = "75 years of age"
)

library(openxlsx)
test_instruments <- read.xlsx("instrument_table_2.xlsx", sheet = 1)
names(test_instruments) <- c("Label", "Instrument", "Cognitive function/s assessed", "References")

#gt::gt(test_instruments)
sjPlot::tab_df(test_instruments)
```

```{r}
ggplot(dplyr::filter(long0, phase == 1), aes(x = age_1, y = value)) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2)) +
  scale_color_manual(values = c("orange3", "slategrey")) +
  facet_wrap(~test, labeller = as_labeller(test_names)) +
  xlab("Age (years)") +
  ylab("Score (z)") +
  theme_bw()


```

