---
title: "Supplementary materials"
author: "Bindoff, A. D., Summers, M. J., Hill, E., Alty, J., Vickers, J. C."
date: "2020-06-17"
output:
  html_document: default
---

Accompanies the article "Later-life education slows cognitive decline: a long-term prospective interventional study"  
\


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r}
library(dplyr)
library(sjPlot)
library(glmmTMB)
library(lme4)

long0 <- readRDS('thbp_7yr_long_20200617.rds')


models <- readRDS("adj_unadj.rds")

tab_anova <- function(model, digits = 1, eps = .001){
  sjPlot::tab_df(broom::tidy(car::Anova(model)) %>%
                   dplyr::rename('Chi.sq' = statistic,
                                 Term = term) %>%
                   dplyr::mutate(p.value = format.pval(p.value, digits = digits, eps = eps)),
                 digits = digits)
}

tab_F <- function(model, digits = 1, eps = .001){
  sjPlot::tab_df(broom::tidy(anova(model)) %>%
                   dplyr::rename('Term' = term,
                                 'F' = statistic,
                                 'num. df' = NumDF,
                                 'denom. df' = DenDF,
                                 'SS' = sumsq) %>%
                   select(-meansq) %>%
                   dplyr::mutate(p.value = format.pval(p.value, digits = digits, eps = eps)),
                 digits = digits)
}

```

## {.tabset}

### Table S1. 


```{r}
tab_anova(models$m2.un)
```
  
\

  
```{r}
tab_anova(models$m2.adj)
```
  
  
\

```{r}
tab_model(models$m2.un, models$m2.adj, digits = 3, show.p = FALSE)


```
\

  
Experimental group trajectories for each cognitive test instrument, with and without adjustment for prior cognitive reserve and age. Reported p-values are taken from analysis of deviance tables. Tables of coefficients are also shown which include 95% confidence intervals.  
  
   
  

### Table S2.

```{r}
library(emmeans)
j <- emtrends(models$m2.adj, pairwise ~ group | test, var = "Time", show.levels = TRUE)
j
```
\

  
Estimated marginal mean trends for experimental groups, adjusted for prior cognitive reserve and age.  


### Table S3.  

```{r}
tab_model(models$m3.adj, digits = 3)
```
\

  
  
Three-way age x Time x group interaction, adjusted for prior cognitive reserve.  


### Table S4.  

```{r}
tab_anova(models$m4.un)
```
\

     
     
```{r}
tab_model(models$m4.un, digits = 3, show.p = FALSE)
```
\

  
```{r}
m4.adj <- lmer(Score ~ `Prior CR` + scale(age_1) + Time*test*scale(`Academic Load`) + (1|Participant), long0)
tab_anova(m4.adj)

```
\
  
  
  
Testing the association between academic load (in %FTE) and cognitive test-specific trajectories, adjusted for age and prior cognitive reserve.  

### Table S5.  

```{r}
tab_F(models$m5.un)
```
\
  
  
  
```{r}
tab_F(models$m5.adj)
```
\
  
  
  
```{r}
tab_model(models$m5.un, models$m5.adj, digits = 3, show.p = FALSE)

```
\
  
  
  
Testing the association between prior cognitive reserve and experimental group trajectories, with and without adjusting for the main effect of age and the interaction between age and Time.  
  
  