---
title: "Supplementary materials"
author: "Bindoff, A."
date: "17/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r}
library(dplyr)
library(sjPlot)
library(glmmTMB)
library(lme4)

long0 <- readRDS('thbp_7yr_long_20200617.rds')


models <- readRDS("adj_unadj.rds")

```

## {.tabset}

### Table S1. 


```{r}
car::Anova(models$m2.un)
car::Anova(models$m2.adj)

tab_model(models$m2.un, models$m2.adj, digits = 3, show.p = FALSE)


```

Experimental group trajectories for each cognitive test instrument, with and without adjustment for prior cognitive reserve and age. Reported p-values are taken from analysis of deviance tables. Tables of coefficients are also shown which include 95% confidence intervals.  


### Table S2.

```{r}
library(emmeans)
j <- emtrends(models$m2.adj, pairwise ~ group | test, var = "Time", show.levels = TRUE)
j
```

Estimated marginal mean trends for experimental groups, adjusted for prior cognitive reserve and age.  


### Table S3.  

```{r}
tab_model(models$m3.adj, digits = 3)
```

Three-way age x Time x group interaction, adjusted for prior cognitive reserve. 

### Table S4.  

```{r}
car::Anova(models$m4.un, '2')
tab_model(models$m4.un, digits = 3, show.p = FALSE)

m4.adj <- lmer(Score ~ `Prior CR` + scale(age_1) + Time*test*scale(`Academic Load`) + (1|Participant), long0)
car::Anova(m4.adj, '2')

```

Testing the association between academic load (in %FTE) and cognitive test-specific trajectories, adjusted for age and prior cognitive reserve.  

### Table S5.  

```{r}
anova(models$m5.un)
anova(models$m5.adj)

tab_model(models$m5.un, models$m5.adj, digits = 3, show.p = FALSE)

```

Testing the association between prior cognitive reserve and experimental group trajectories, with and without adjusting for the main effect of age and the interaction between age and Time.  



